\documentclass[11pt]{letter}
\topmargin = 0.0in
\oddsidemargin = 0.0 in
\evensidemargin = 0.0 in
\textwidth = 7.0 in
\marginparwidth = 0.0 in
\headheight = 0 pt
\headsep = 0 pt
\textheight = 10.0 in
\pagenumbering{gobble}
\usepackage[colorlinks = True] {hyperref}
\usepackage[margin=0.2in]{geometry}
\begin{document}
\centerline{\large \bf Alyssa H. Smith}
\smallskip
\centerline{\large{ 3 Ames Street Apt. Wa209 $\bullet$ Cambridge, MA 02142 $\bullet$ (401)-688-2239}}
\smallskip
\centerline{\large Email: asmithh@mit.edu $\bullet$ Github: asmithh $\bullet$ Website: asmithh.scripts.mit.edu/main.html} 
\hrulefill


\noindent {\large \bf Education}
\newline
\noindent {\bf Massachusetts Institute of Technology \hskip 270pt Cambridge, MA}
\newline 
\noindent{ Bachelor's of Science. Cumulative GPA: 4.8 \hskip 270pt expected June 2017
\newline 
\noindent {\bf Spring 2016 courses}: 
\newline Comparative Media Studies Thesis; Current Debates in Media; Aero-Astro Experimental Projects II; Geometric Folding Algorithms
\newline
\noindent{\bf Previous Relevant Courses:}
\newline
Design and Analysis of Algorithms; Introduction to Machine Learning; Introduction to Inference; Linear Algebra; Introduction to Algorithms; Advanced Natural Language Processing; Online Machine Learning Algorithms; Network Cultures; Qualitative Methods; Aero-Astro Experimental Projects I
\smallskip

\noindent{\large \bf Skills}
\newline
\noindent{\bf Programming Languages: } Languages: Python, XML, Java, Javascript, HTML, Processing. 
\newline
\noindent {\bf Programming (and related) Skills:} web scraping, machine learning, network analysis, data cleaning, Twitter bots, databases, natural language processing, SQL, Git, Numpy, Pandas, scikit-learn, scipy
\newline 
\noindent{\bf Foreign Languages} French (conversation); Japanese (basic)
\smallskip


\noindent {\large \bf Relevant Experience }
\newline
\noindent{\bf Point. Software Engineer \hskip 205pt Cambridge, MA -- September 2016 - present}
\newline Created machine learning models to help build an intelligent email client as part of the initial software team of this young startup.  
\newline
\noindent{\bf Tumblr Product Analytics Intern \hskip 215pt New York, NY -- Summer 2016}
\newline Produced actionable insights through analysis of user data.  Created a neural network language model of tags and clustered users based on site usage data.  
\newline
\noindent{\bf Japanese Parser Undergraduate Research \hskip 190pt Cambridge, MA -- Fall 2015}
\newline Developed a corpus-based contextual browsing system and API to help Japanese language learners understand correct usage.  Collaborated with a front-end developer to coordinate backend format with output in browsing system.
\newline
\noindent{\bf Berkman Center Summer Intern \hskip 207pt Cambridge, MA -- Summer 2015}
\newline 
Assessed the efficacy of municipal broadband programs in Massachusetts; published a MediaCloud \href{http://mediacloud.org/2015/11/04/the-meaning-of-common-links-in-media-conflict-bridges-or-hate-links/}{\color{blue} blog post} analyzing media coverage of the GamerGate controversy.
\newline
\noindent{\bf Open Technology Institute \hskip 245pt Washington, DC -- January 2015}
\newline
Completed statistical analysis of broadband availability and adoption data to understand where and why gaps in access arise; worked on scraping data for OTI's annual Cost of Connectivity report.  
\newline
\noindent{\bf Center for Civic Media UROP \hskip 165pt Cambridge, MA -- Fall 2014 - Spring 2015}
\newline Investigated how journalists' Twitter data can predict who they quote in their articles in order to affect gender bias in journalist citations.

\noindent {\large \bf Leadership and Projects}
\newline 
\noindent{\bf HKN Tutoring \hskip 340pt Cambridge, MA -- Spring 2016}
\newline Tutored peers for an introductory machine learning course.
\newline
\noindent{\bf MIT Committee on Curricula \hskip 260pt Cambridge, MA -- Fall 2015}
\newline Discussed changes to the curriculum and major programs; reviewed policy changes and suggested modifications to policies.
\newline
\noindent{\bf Co-chair, Academic Advisory Committee \hskip 210pt Cambridge, MA -- Fall 2015}
\newline Implemented improvements to the advising system and the undergraduate academic experience; coordinated with administration to figure out best practices and plan joint efforts.
\newline
\noindent{\bf HackMIT \hskip 340pt Cambridge, MA -- September 2015}
\newline Built a glove that powered a Twitter bot by using sensor data as a source of randomness.




\end{document}